---
title: "Simulation Analyses"
author: Sam Woodman
output: html_document
---

```{r}
library(dplyr)
# setwd("~/Google Drive/Semester 8/Thesis/NetLogo+R GitHub/NetLogo R Analyses/Sim Analyses4")

# Simulation data
all.data <- read.csv("Bees sim_all4-table.csv", skip = 6, stringsAsFactors=FALSE)

# Data calculation
all.data$energy.bee <- all.data$hive.collected / all.data$population
all.data$log.energy.bee <- log(all.data$energy.bee)
all.data$dance.avg <- all.data$dance.quality / all.data$dance.quantity
all.data$random.avg <- all.data$random.quality / all.data$random.quantity
all.data$avg.diff <-all.data$dance.avg - all.data$random.avg

# Data cleanup
names(all.data)[4] <- "communication"
all.data$communication <- as.factor(all.data$communication)
all.data$population <- as.factor(all.data$population)
all.data$environment <- as.factor(sapply(1:nrow(all.data), 
                                         function(i) {i <- paste(substr(all.data$resource_density[i],2,2), 
                                                                 ": ", substr(all.data$R_value[i], 2,4), 
                                                                 sep = "")}))

# Dense
dense.data <- all.data %>% filter(resource_density == "\"dense\"")
dense.data$environment <- as.factor(as.character(dense.data$environment))
# Sparse
sparse.data <- all.data %>% filter(resource_density == "\"sparse\"")
sparse.data$environment <- as.factor(as.character(sparse.data$environment))
# Comm
comm.data <- all.data %>% filter(communication == TRUE)

# New table for dance and random avg quality
dance.data <- data.frame(energy.avg = comm.data$dance.avg, environment = comm.data$environment, 
                         communication = comm.data$communication, population = comm.data$population,
                         id.method = rep("dance", length(comm.data[,1])))
random.data <- data.frame(energy.avg = comm.data$random.avg, environment = comm.data$environment, 
                         communication = comm.data$communication, population = comm.data$population,
                         id.method = rep("random", length(comm.data[,1])))
avg.data <- rbind(dance.data, random.data)
```

## Plots of the simulation runs

```{r}
# Plot results
boxplot(energy.bee ~ communication+population+environment, data=all.data, 
        col = c("green", "red", "brown", "blue"), las = 2, main = "All simulations", 
        xlab = "Resource density (R value)", ylab = "Energy(J)/bee", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0",
                  "0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topright", pch = 15, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))

boxplot(energy.bee ~ communication+population+environment, data=all.data, log = "y", 
        col = c("green", "red", "brown", "blue"), las = 2, main = "Log plot of energy collected (J) per bee", 
        xlab = "Resource density (R value)", ylab = "Energy(J)/bee", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0",
                  "0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topright", pch = 15, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
```


## Data Analyses-Testing for an interaction effect with ANOVAs

Now for the actual data analysis. We will perform anova tests to test for first significant pairwise interactions between colony size, communication, and environment and then for all factors (wording-fix).

### 1. Colony size and communication
```{r}
null <- lm(log.energy.bee ~ population+communication+environment, data = all.data)
alt.1a <- lm(log.energy.bee ~ population*communication+environment, data = all.data)
anova(null, alt.1a)
```

### 2. Colony size and environment
```{r}
alt.1b <- lm(log.energy.bee ~ population*environment+communication, data = all.data)
anova(null, alt.1b)
```

### 3. Communication and environment
```{r}
alt.1c <- lm(energy.bee ~ population+communication*environment, data = all.data)
anova(lm(energy.bee ~ population+communication+environment, data = all.data), alt.1c)
```

### 4. Colony size, communication, and environment
```{r}
null.all.1 <- lm(log.energy.bee ~ population + communication + environment + 
                   population*communication + population*environment + communication*environment, data = all.data)
alt.all.1 <- lm(log.energy.bee ~ population*communication*environment, data = all.data)
anova(null.all.1, alt.all.1)
```


## Other
### Found vs Untouched
Proportion of resources that are found
```{r}
boxplot((resources.found/resources) ~ communication+population+environment, data=all.data, 
        col = c("green", "red", "brown", "blue"), las = 2, main = "", 
        xlab = "Resource density (R value)", ylab = "", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0",
                  "0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topleft", pch = 15, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
```

```{r}
# found.all
null.2 <- glm(cbind(resources.found, resources.untouched) ~ population+communication+environment, 
              family = binomial(), data = all.data)
alt.2a <- glm(cbind(resources.found, resources.untouched) ~ population*communication+environment, 
              family = binomial(), data = all.data)
anova(null.2, alt.2a, test="Chisq")

alt.2b <- glm(cbind(resources.found, resources.untouched) ~ population+communication*environment, 
              family = binomial(), data = all.data)
anova(null.2, alt.2b, test="Chisq")

alt.2c <- glm(cbind(resources.found, resources.untouched) ~ population*environment+communication, 
              family = binomial(), data = all.data)
anova(null.2, alt.2c, test="Chisq")
```

```{r}
null.all.2 <- glm(cbind(resources.found, resources.untouched) ~ population + communication + environment + 
                    population*communication + population*environment + communication*environment, 
                  family = binomial(), data = all.data)
alt.all.2 <- glm(cbind(resources.found, resources.untouched) ~ population*environment*communication, 
                 family = binomial(), data = all.data)
anova(null.all.2, alt.all.2, test="Chisq")
```

### Depleted vs Found and not depleted
```{r}
boxplot((resources.depleted/resources.found) ~ communication+population+environment, data=all.data, 
        col = c("green", "red", "brown", "blue"), las = 2, main = "", 
        xlab = "Resource density (R value)", ylab = "", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0",
                  "0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topleft", pch = 15, cex = 0.55, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
```

```{r}
# found.all
null.3 <- glm(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                population+communication+environment, 
              family = binomial(), data = all.data)
alt.3a <- glm(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                population*communication+environment, 
              family = binomial(), data = all.data)
anova(null.3, alt.3a, test="Chisq")

alt.3b <- glm(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                population+communication*environment, 
              family = binomial(), data = all.data)
anova(null.3, alt.3b, test="Chisq")

alt.3c <- glm(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                population*environment+communication, 
              family = binomial(), data = all.data)
anova(null.3, alt.3c, test="Chisq")
```

```{r}
null.all.3 <- glm(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                    population + communication + environment + 
                    population*communication + population*environment + communication*environment, 
                  family = binomial(), data = all.data)
alt.all.3 <- glm(cbind(resources.depleted, (resources.found-resources.depleted)) ~
                   population*environment*communication, 
                 family = binomial(), data = all.data)
anova(null.all.3, alt.all.3, test="Chisq")
```

### Avg Random Quality vs Avg Dance Quality

#### Plots
```{r}
plot(x = all.data$dance.avg, y = all.data$random.avg)
abline(a = 0, b = 1)

boxplot(avg.diff ~ population+environment, data=comm.data, 
        col = c("green", "red"), las = 2, main = "Simulations with communication", 
        xlab = "Resource density (R value)", ylab = "Energy(J)/bee", 
        ylim = c(60, 250), 
        names = c("0.4", "0.4",
                  "0.6", "0.6",
                  "0.8", "0.8",
                  "1.0", "1.0",
                  "0.4", "0.4",
                  "0.6", "0.6",
                  "0.8", "0.8",
                  "1.0", "1.0"))
legend("topright", pch = 15, col = c("green", "red", "brown", "blue"), 
       c("Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))

```

#### 1. Colony size and communication
```{r}
#null <- glm(cbind(dance.avg, random.avg) ~ population+communication+environment, data = all.data[!is.na(all.data$dance.avg),])
#alt.1a <- lm(log.energy.bee ~ population*communication+environment, data = all.data)
#anova(null, alt.1a)
```

#### 2. Colony size and environment
```{r}
#alt.1b <- lm(log.energy.bee ~ population*environment+communication, data = all.data)
#anova(null, alt.1b)
```

#### 3. Communication and environment
```{r}
#alt.1c <- lm(energy.bee ~ population+communication*environment, data = all.data)
#anova(lm(energy.bee ~ population+communication+environment, data = all.data), alt.1c)
```

#### 4. Colony size, communication, and environment
```{r}
#null.all.1 <- lm(log.energy.bee ~ population + communication + environment + 
#                   population*communication + population*environment + communication*environment, data = all.data)
#alt.all.1 <- lm(log.energy.bee ~ population*communication*environment, data = all.data)
#anova(null.all.1, alt.all.1)
```

