---
title: "Simulation Analyses"
author: Sam Woodman
output: html_document
---

```{r}
library(dplyr)
library(lme4)
# setwd("~/Google Drive/Semester 8/Thesis/NetLogo+R GitHub/NetLogo R Analyses/Sim Analyses5")

# Simulation data
all.data <- read.csv("Bees sim_all5-table.csv", skip = 6, stringsAsFactors=FALSE)
all.data <- all.data %>% filter(resource_density == "\"sparse\"")

### all.data IS ONLY SPARSE DATA ###

# Data names
names(all.data)[4] <- "communication"
names(all.data)[19] <- "max.dist"

# Data calculation
all.data$energy.bee <- all.data$hive.collected / all.data$population
all.data$log.energy.bee <- log(all.data$energy.bee)
all.data$energy.trip <- all.data$hive.collected / all.data$foraged.count
all.data$log.energy.trip <- log(all.data$energy.trip)
all.data$dance.avg <- all.data$dance.quality / all.data$dance.quantity
all.data$random.avg <- all.data$random.quality / all.data$random.quantity
all.data$avg.diff <- all.data$dance.avg - all.data$random.avg
all.data$max.dist.km <- all.data$max.dist * 6.67 / 1000

# Data cleanup
all.data$communication <- as.factor(all.data$communication)
all.data$population <- as.factor(all.data$population)
all.data$environment <- as.factor(sapply(1:nrow(all.data), 
                                         function(i) {i <- substr(all.data$R_value[i], 2,4)}))


# Comm
comm.data <- all.data %>% filter(communication == TRUE)

# New table for dance and random avg quality
dance.data <- data.frame(energy.avg = comm.data$dance.avg, environment = comm.data$environment, 
                         communication = comm.data$communication, population = comm.data$population,
                         repetitions = comm.data$repetitions, id.method = rep("dance", length(comm.data[,1])))
random.data <- data.frame(energy.avg = comm.data$random.avg, environment = comm.data$environment, 
                          communication = comm.data$communication, population = comm.data$population,
                          repetitions = comm.data$repetitions, id.method = rep("random", length(comm.data[,1])))
avg.data <- rbind(dance.data, random.data)
```

## Plots of the simulation runs

```{r}
# Plot results
boxplot(energy.bee ~ communication+population+environment, data=all.data, 
        col = c("green", "red", "brown", "blue"), las = 2, main = "", cex.axis = 0.8, 
        xlab = "Resource distribution (R value)", ylab = "Energy(J) collected/bee", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topright", pch = 15, cex = 0.8, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
axis(1, at = c(0.5, 16.5, 32.5), labels = c("", "", ""), line = 2.05)
axis(1, at = c(8, 24), labels = c("Dense", "Sparse"), line = 0.9, tick = FALSE, cex.axis = 0.8)


boxplot(energy.bee ~ communication+population+environment, data=all.data, log = "y", 
        col = c("green", "red", "brown", "blue"), las = 2, main = "", cex.axis = 0.8, 
        xlab = "Resource distribution (R value)", ylab = "Energy(J) collected/bee", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topright", pch = 15, cex = 0.8, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
axis(1, at = c(0.5, 16.5, 32.5), labels = c("", "", ""), line = 2.05)
axis(1, at = c(8, 24), labels = c("Dense", "Sparse"), line = 0.9, tick = FALSE, cex.axis = 0.8)


boxplot(energy.trip ~ communication+population+environment, data=all.data, log = "y", 
        col = c("green", "red", "brown", "blue"), las = 2, main = "", cex.axis = 0.8, 
        xlab = "Resource distribution (R value)", ylab = "energy/trip", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topright", pch = 15, cex = 0.8, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
axis(1, at = c(0.5, 16.5, 32.5), labels = c("", "", ""), line = 2.05)
axis(1, at = c(8, 24), labels = c("Dense", "Sparse"), line = 0.9, tick = FALSE, cex.axis = 0.8)
```


## Data Analyses-Testing for an interaction effect with ANOVAs

Now for the actual data analysis. We will perform anova tests to test for first significant pairwise interactions between colony size, communication, and environment and then for all factors (wording-fix).

### Per bee
### Colony Size
```{r}
null.0 <- lmer(log.energy.bee ~ 1+(1|repetitions), data = all.data)
alt.0a <- lmer(log.energy.bee ~ population+(1|repetitions), data = all.data)
anova(null.0, alt.0a)
```

### Communication
```{r}
alt.0b <- lmer(log.energy.bee ~ communication+(1|repetitions), data = all.data)
anova(null.0, alt.0b)
```

### Environment
```{r}
alt.0c <- lmer(log.energy.bee ~ environment+(1|repetitions), data = all.data)
anova(null.0, alt.0c)
```

### 1. Colony size and communication
```{r}
null.1 <- lmer(log.energy.bee ~ population+communication+environment+(1|repetitions), data = all.data)
alt.1a <- lmer(log.energy.bee ~ population*communication+environment+(1|repetitions), data = all.data)
anova(null.1, alt.1a)
```

### 2. Colony size and environment
```{r}
alt.1b <- lmer(log.energy.bee ~ population*environment+communication+(1|repetitions), data = all.data)
anova(null.1, alt.1b)
```

### 3. Communication and environment
```{r}
alt.1c <- lmer(log.energy.bee ~ population+environment*communication+(1|repetitions), data = all.data)
anova(null.1, alt.1c)
```

### 4. Colony size, communication, and environment
```{r}
null.all.1 <- lmer(log.energy.bee ~ population + communication + environment + 
                     population*communication + population*environment + communication*environment +
                     (1|repetitions), data = all.data)
alt.all.1 <- lmer(log.energy.bee ~ population*communication*environment+(1|repetitions), data = all.data)
anova(null.all.1, alt.all.1)
```


### Per trip
### Colony Size
```{r}
null.0 <- lmer(log.energy.trip ~ 1+(1|repetitions), data = all.data)
alt.0a <- lmer(log.energy.trip ~ population+(1|repetitions), data = all.data)
anova(null.0, alt.0a)
```

### Communication
```{r}
alt.0b <- lmer(log.energy.trip ~ communication+(1|repetitions), data = all.data)
anova(null.0, alt.0b)
```

### Environment
```{r}
alt.0c <- lmer(log.energy.trip ~ environment+(1|repetitions), data = all.data)
anova(null.0, alt.0c)
```

### 1. Colony size and communication
```{r}
null.1 <- lmer(log.energy.trip ~ population+communication+environment+(1|repetitions), data = all.data)
alt.1a <- lmer(log.energy.trip ~ population*communication+environment+(1|repetitions), data = all.data)
anova(null.1, alt.1a)
```

### 2. Colony size and environment
```{r}
alt.1b <- lmer(log.energy.trip ~ population*environment+communication+(1|repetitions), data = all.data)
anova(null.1, alt.1b)
```

### 3. Communication and environment
```{r}
alt.1c <- lmer(log.energy.trip ~ population+environment*communication+(1|repetitions), data = all.data)
anova(null.1, alt.1c)
```

### 4. Colony size, communication, and environment
```{r}
null.all.1 <- lmer(log.energy.trip ~ population + communication + environment + 
                     population*communication + population*environment + communication*environment + 
                     (1|repetitions), data = all.data)
alt.all.1 <- lmer(log.energy.trip ~ population*communication*environment+(1|repetitions), data = all.data)
anova(null.all.1, alt.all.1)
```

## Other
### Found vs Untouched
Proportion of resources that are found
```{r}
boxplot((resources.found/resources) ~ communication+population+environment, data=all.data, 
        col = c("green", "red", "brown", "blue"), las = 2, main = "", cex.axis = 0.8, 
        xlab = "Resource distribution (R value)", ylab = "", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topleft", pch = 15, cex = 0.8, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
axis(1, at = c(0.5, 16.5, 32.5), labels = c("", "", ""), line = 2.05)
axis(1, at = c(8, 24), labels = c("Dense", "Sparse"), line = 0.9, tick = FALSE, cex.axis = 0.8)
```

#### Population * Communication
```{r}
null.2 <- glmer(cbind(resources.found, resources.untouched) ~ population+communication+environment+(1|repetitions), 
                family = binomial(), data = all.data)
alt.2a <- glmer(cbind(resources.found, resources.untouched) ~ population*communication+environment+(1|repetitions), 
                family = binomial(), data = all.data)
anova(null.2, alt.2a, test="Chisq")
```

#### Communication * Environment
```{r}
alt.2b <- glmer(cbind(resources.found, resources.untouched) ~ population+communication*environment+(1|repetitions), 
                family = binomial(), data = all.data)
anova(null.2, alt.2b, test="Chisq")
```

#### Population * Environment
```{r}
alt.2c <- glmer(cbind(resources.found, resources.untouched) ~ population*environment+communication+(1|repetitions), 
                family = binomial(), data = all.data)
anova(null.2, alt.2c, test="Chisq")
```

#### Population * Environment * Communication
```{r}
null.all.2 <- glmer(cbind(resources.found, resources.untouched) ~ population + communication + environment + 
                      population*communication + population*environment + communication*environment +
                      (1|repetitions), 
                    family = binomial(), data = all.data)
alt.all.2 <- glmer(cbind(resources.found, resources.untouched) ~ population*environment*communication+(1|repetitions), 
                   family = binomial(), data = all.data)
anova(null.all.2, alt.all.2, test="Chisq")
```


### Depleted vs Found and not depleted
#### Plot
```{r}
boxplot((resources.depleted/resources.found) ~ communication+population+environment, data=all.data, 
        col = c("green", "red", "brown", "blue"), las = 2, main = "", cex.axis = 0.8, 
        xlab = "Resource distribution (R value)", ylab = "", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topleft", pch = 15, cex = 0.55, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
axis(1, at = c(0.5, 16.5, 32.5), labels = c("", "", ""), line = 2.05)
axis(1, at = c(8, 24), labels = c("Dense", "Sparse"), line = 0.9, tick = FALSE, cex.axis = 0.8)
```

#### Population * Communication
```{r}
null.3 <- glmer(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                  population+communication+environment+(1|repetitions), 
                family = binomial(), data = all.data)
alt.3a <- glmer(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                  population*communication+environment+(1|repetitions), 
                family = binomial(), data = all.data)
anova(null.3, alt.3a, test="Chisq")
```

#### Communication * Environment
```{r}
alt.3b <- glmer(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                  population+communication*environment+(1|repetitions), 
                family = binomial(), data = all.data)
anova(null.3, alt.3b, test="Chisq")
```

#### Population * Environment
```{r}
alt.3c <- glmer(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                  population*environment+communication+(1|repetitions), 
                family = binomial(), data = all.data)
anova(null.3, alt.3c, test="Chisq")
```

#### Population * Environment * Communication
```{r}
null.all.3 <- glmer(cbind(resources.depleted, (resources.found-resources.depleted)) ~ 
                      population + communication + environment + 
                      population*communication + population*environment + communication*environment +
                      (1|repetitions), 
                    family = binomial(), data = all.data)
alt.all.3 <- glmer(cbind(resources.depleted, (resources.found-resources.depleted)) ~
                     population*environment*communication+(1|repetitions), 
                   family = binomial(), data = all.data)
anova(null.all.3, alt.all.3, test="Chisq")
```

### Avg Random Quality vs Avg Dance Quality

#### Plot
```{r}
# plot(x = all.data$dance.avg, y = all.data$random.avg)
# abline(a = 0, b = 1)

boxplot(energy.avg ~ id.method+population+environment, data=avg.data, 
        col = c("green", "red", "brown", "blue"), las = 2, cex.axis = 0.8, main = "", 
        xlab = "Resource distribution (R value)", ylab = "Average Energy(J)/dancing or foraging event", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topright", pch = 15, cex = 0.8, col = c("green", "red", "brown", "blue"), 
       c("Dance, Pop=500", "Rand, Pop=500", "Dance, Pop=3000", "Rand, Pop=3000"))
axis(1, at = c(0.5, 16.5, 32.5), labels = c("", "", ""), line = 2.05)
axis(1, at = c(8, 24), labels = c("Dense", "Sparse"), line = 0.9, tick = FALSE, cex.axis = 0.8)
```

#### 1. Population * Method
```{r}
null.4 <- lmer(energy.avg ~ population+id.method+environment+(1|repetitions), data = avg.data)
alt.4a <- lmer(energy.avg ~ population*id.method+environment+(1|repetitions), data = avg.data)
anova(null.4, alt.4a)
```

#### 2. Population * environment
```{r}
alt.4b <- lmer(energy.avg ~ population*environment+id.method+(1|repetitions), data = avg.data)
anova(null.4, alt.4b)
```

#### 3. Method * environment
```{r}
alt.4c <- lmer(energy.avg ~ population+id.method*environment+(1|repetitions), data = avg.data)
anova(null.4, alt.4c)
```

#### 4. Population * communication * environment
```{r}
null.all.4 <- lmer(energy.avg ~ population + id.method + environment + 
                     population*id.method + population*environment + id.method*environment +
                     (1|repetitions), data = avg.data)
alt.all.4 <- lmer(energy.avg ~ population*id.method*environment+(1|repetitions), data = avg.data)
anova(null.all.4, alt.all.4)
```

#### Difference between averages
```{r}
anova(lmer((dance.avg-random.avg) ~ environment+population+(1|repetitions), data = comm.data),
      lmer((dance.avg-random.avg) ~ environment*population+(1|repetitions), data = comm.data))
```


### Quality of resources found through random searching

#### Plot
```{r}
boxplot(random.avg ~ communication+population+environment, data=all.data, 
        col = c("green", "red", "brown", "blue"), las = 2, cex.axis = 0.8, main = "All simulations-random avg", 
        xlab = "Resource distribution (R value)", ylab = "Energy(J)/resource found", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topright", pch = 15, cex = 0.8, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
axis(1, at = c(0.5, 16.5, 32.5), labels = c("", "", ""), line = 2.05)
axis(1, at = c(8, 24), labels = c("Dense", "Sparse"), line = 0.9, tick = FALSE, cex.axis = 0.8)
```


#### 1. Colony size and communication
```{r}
null.5 <- lmer(random.avg ~ population+communication+environment+(1|repetitions), data = all.data)
alt.5a <- lmer(random.avg ~ population*communication+environment+(1|repetitions), data = all.data)
anova(null.5, alt.5a)
```

#### 2. Colony size and environment
```{r}
alt.5b <- lmer(random.avg ~ population*environment+communication+(1|repetitions), data = all.data)
anova(null.5, alt.5b)
```

#### 3. Communication and environment
```{r}
alt.5c <- lmer(random.avg ~ population+communication*environment+(1|repetitions), data = all.data)
anova(null.5, alt.5c)
```

#### 4. Colony size, communication, and environment
```{r}
null.all.5 <- lmer(random.avg ~ population + communication + environment + 
                     population*communication + population*environment + communication*environment +
                     (1|repetitions), data = all.data)
alt.all.5 <- lmer(random.avg ~ population*communication*environment+(1|repetitions), data = all.data)
anova(null.all.5, alt.all.5)
```



### Max distance from hive

#### Plot
```{r}
boxplot(max.dist.km ~ communication+population+environment, data=all.data, 
        col = c("green", "red", "brown", "blue"), las = 2, cex.axis = 0.8, main = "", 
        xlab = "Resource distribution (R value)", ylab = "Kilometers", 
        names = c("0.4", "0.4", "0.4", "0.4",
                  "0.6", "0.6", "0.6", "0.6",
                  "0.8", "0.8", "0.8", "0.8",
                  "1.0", "1.0", "1.0", "1.0"))
legend("topleft", pch = 15, cex = 0.8, col = c("green", "red", "brown", "blue"), 
       c("Comm=F, Pop=500", "Comm=T, Pop=500", "Comm=F, Pop=3000", "Comm=T, Pop=3000"))
axis(1, at = c(0.5, 16.5, 32.5), labels = c("", "", ""), line = 2.05)
axis(1, at = c(8, 24), labels = c("Dense", "Sparse"), line = 0.9, tick = FALSE, cex.axis = 0.8)
```


#### 1. Colony size and communication
```{r}
null.6 <- lmer(max.dist.km ~ population+communication+environment+(1|repetitions), data = all.data)
alt.6a <- lmer(max.dist.km ~ population*communication+environment+(1|repetitions), data = all.data)
anova(null.6, alt.6a)
```

#### 2. Colony size and environment
```{r}
alt.6b <- lmer(max.dist.km ~ population*environment+communication+(1|repetitions), data = all.data)
anova(null.5, alt.6b)
```

#### 3. Communication and environment
```{r}
alt.6c <- lmer(max.dist.km ~ population+communication*environment+(1|repetitions), data = all.data)
anova(null.6, alt.6c)
```

#### 4. Colony size, communication, and environment
```{r}
null.all.6 <- lmer(max.dist.km ~ population + communication + environment + 
                     population*communication + population*environment + communication*environment +
                     (1|repetitions), data = all.data)
alt.all.6 <- lmer(max.dist.km ~ population*communication*environment+(1|repetitions), data = all.data)
anova(null.all.6, alt.all.6)

